DATA 621 - HW1 - Regression Model

### 2020-09-10 HW1/Regression Model - Deokinanan.rmd
Code added to get data from Git

# Load training data set
train_df = read.csv("C:/Users/Deokinanan/Desktop/2019 -2021 CUNY SPS/FALL 2020/DATA 621/WEEK 3/moneyball-training-data.csv")
train_df = subset(train_df, select = -c(INDEX))
```

@@

After the steps, the final model resulted below, with $adj. R^2 = 0.42$, suggesting that this model accounts for nearly 42% of the variation in the dependent variable with the independent variables, which is acceptable as a good model. Within the method of `lmStepAIC`, AIC (Akaike Information Criteria) quantifies the amount of information loss due to simplification. That is, based on the AIC, the final model outputted is the simplest model without impacting much on the performance.

@@

```{r message=FALSE, warning=FALSE}
# load the test data
test_df = read.csv("C:/Users/Deokinanan/Desktop/2019 -2021 CUNY SPS/FALL 2020/DATA 621/WEEK 3/moneyball-evaluation-data.csv")

>>>>

# Load training data set
theURL = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/HW1/data/moneyball-training-data.csv"
train_df = data.frame(read.csv(file = theURL, header = TRUE, sep = ","))
train_df = subset(train_df, select = -c(INDEX))
```

@@

After the steps, the final model resulted below, with $adj. R^2 = 0.43$, suggesting that this model accounts for nearly 42% of the variation in the dependent variable with the independent variables, which is acceptable as a good model. Within the method of `lmStepAIC`, AIC (Akaike Information Criteria) quantifies the amount of information loss due to simplification. That is, based on the AIC, the final model outputted is the simplest model without impacting much on the performance.

@@

```{r message=FALSE, warning=FALSE}
# load the test data
theURL = "https://raw.githubusercontent.com/aadler/DT621_Fall2020_Group2/master/HW1/data/moneyball-evaluation-data.csv"
test_df = data.frame(read.csv(file = theURL, header = TRUE, sep = ","))
